Verifying Demonstrations

### 2018-11-14 paper/verifiability-analysis.tex
Edits linkability in verifiability analysis

\Cref{CountOnce} is required to prevent Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
This possibility is prevented by the use of \(\pid\).
Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key \(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.

>>>>

\Cref{CountOnce} is required to prevent Sybil attacks, in the sense
that Alice cannot provide two (or more) participation proofs for a
specific protest and thus be counted more than once.
This possibility is prevented by the use of \(\pid\).
Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) such that the verifier\footnote{%
  Here the verifier is either the witness during the distance bounding or the 
  verifier who tries to verify the count.
} accepts the proof
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.
